High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-05-15 notebooks/gmsc.qmd
uh
rerun

# Data:
test_size = 0.2
n_obs = Int(10000 / (1.0 - test_size))
counterfactual_data, test_data = train_test_split(load_gmsc(n_obs); test_size=test_size)
X, y = CounterfactualExplanations.DataPreprocessing.unpack_data(counterfactual_data)
X = table(permutedims(X))
labels = counterfactual_data.output_encoder.labels
input_dim, n_obs = size(counterfactual_data.X)
output_dim = length(unique(labels))
```

@@

```{julia}
# Model parameters:
epochs = 100
batch_size = minimum([Int(round(n_obs/10)), 128])
n_hidden = 128
activation = Flux.relu
builder = MLJFlux.@builder Flux.Chain(
    Dense(n_in, n_hidden, activation),
    Dense(n_hidden, n_hidden, activation),
    Dense(n_hidden, n_out),
)
n_ens = 5                                   # number of models in ensemble
_loss = Flux.Losses.crossentropy       # loss function
_finaliser =  Flux.softmax                       # finaliser function
```

```{julia}
# JEM parameters:
𝒟x = Normal()
𝒟y = Categorical(ones(output_dim) ./ output_dim)
sampler = ConditionalSampler(
    𝒟x, 𝒟y, 
    input_size=(input_dim,), 
    batch_size=50,
)
α = [1.0,1.0,1e-1]      # penalty strengths
```

@@

```{julia}
λ₁ = 0.1
λ₂ = 0.5
λ₃ = 0.5
Λ = [λ₁, λ₂, λ₃]

opt = Flux.Optimise.Descent(0.01)
use_class_loss = true

>>>>

# Data:
test_size = 0.2
n_obs = Int(50000 / (1.0 - test_size))
counterfactual_data, test_data = train_test_split(load_gmsc(n_obs); test_size=test_size)
X, y = CounterfactualExplanations.DataPreprocessing.unpack_data(counterfactual_data)
X = table(permutedims(X))
labels = counterfactual_data.output_encoder.labels
input_dim, n_obs = size(counterfactual_data.X)
output_dim = length(unique(labels))
```

@@

```{julia}
# Model parameters:
epochs = 100
batch_size = minimum([Int(round(n_obs/10)), 250])
n_hidden = 128
activation = Flux.swish
builder = MLJFlux.@builder Flux.Chain(
    Dense(n_in, n_hidden, activation),
    Dense(n_hidden, n_hidden, activation),
    Dense(n_hidden, n_out),
)
n_ens = 5                                   # number of models in ensemble
_loss = Flux.Losses.crossentropy       # loss function
_finaliser =  Flux.softmax                       # finaliser function
```

```{julia}
# JEM parameters:
𝒟x = Normal()
𝒟y = Categorical(ones(output_dim) ./ output_dim)
sampler = ConditionalSampler(
    𝒟x, 𝒟y, 
    input_size=(input_dim,), 
    batch_size=10,
)
α = [1.0,1.0,1e-1]      # penalty strengths
```

@@

```{julia}
λ₁ = 0.1
λ₂ = 0.1
λ₃ = 1.0
Λ = [λ₁, λ₂, λ₃]

opt = Flux.Optimise.Descent(0.05)
use_class_loss = false

### 2023-05-15 notebooks/mnist.qmd
rerun

```{julia}
function _plot_eccco_mnist(
    x::Union{AbstractArray, Int}=x_factual, target::Int=target;
    λ=[0.1,0.4,0.4],
    temp=0.1,
    plt_order = ["MLP", "MLP Ensemble", "JEM", "JEM Ensemble"],
    opt = nothing,
    rng::Union{Int,AbstractRNG}=1234,
    T::Int = 100,
    use_class_loss::Bool = true,
)

@@

```{julia}
λ₁ = 0.1
λ₂ = 0.25
λ₃ = 0.25
Λ = [λ₁, λ₂, λ₃]

# Benchmark generators:
generator_dict = Dict(
    "Wachter" => WachterGenerator(λ=λ₁),
    "REVISE" => REVISEGenerator(λ=λ₁),
    "Schut" => GreedyGenerator(),
    "ECCCo" => ECCCoGenerator(λ=Λ),
)
```

>>>>

```{julia}
function _plot_eccco_mnist(
    x::Union{AbstractArray, Int}=x_factual, target::Int=target;
    λ=[0.25,0.75,0.75],
    temp=0.1,
    plt_order = ["MLP", "MLP Ensemble", "JEM", "JEM Ensemble"],
    opt = nothing,
    rng::Union{Int,AbstractRNG}=1234,
    T::Int = 100,
    use_class_loss::Bool = true,
)

@@

```{julia}
Λ = eccco_generator.λ

# Benchmark generators:
generator_dict = Dict(
    "Wachter" => WachterGenerator(λ=Λ[1]),
    "REVISE" => REVISEGenerator(λ=Λ[1]),
    "Schut" => GreedyGenerator(),
    "ECCCo" => eccco_generator,
)
```
